An analysis of Lenin's work: Revolution, war, and fruta

### 2013-11-05 paper/paper.tex
Plot for works.

%% ADDITIONAL OPTIONAL STYLE FILES
%\usepackage[dvips]{graphicx}
%\usepackage{pnastwof}
\usepackage{amssymb,amsfonts,amsmath}
\usepackage[utf8]{inputenc}
\usepackage[activeacute, spanish]{babel}
\selectlanguage{spanish}

@@

In order to reduce noise in the corpus, we filtered all the letters and works that were comparatively little. Our information value theory doesn't work very well with texts with little repetition of words, so we decided to remove texts with less than 1000 words.

*Números (obras totales obtenidas, promedio tokens)
\subsection{Information Value Framework}
*Aclarar settings de Zannette
*Maximización, ventanas
*Cálculo paralelo
*Ajustes de parametros para que concuerden con los resultados de zanette
*doc.top_words()
  representación como set de palabras ponderadas por documento.

@@

*WordnetAnalyzer
  *Synset
  *path, lch, wup
*judge_word
*judge_doc
*judge_year
Dado un conjunto de palabras, definimos la distancia de una palabra a este conjunto como

S(x, C) = max { ... }

>>>>

%% ADDITIONAL OPTIONAL STYLE FILES
%\usepackage[dvips]{graphicx}
%\usepackage{pnastwof}
\usepackage{amssymb,amsfonts,amsmath}
\usepackage[utf8]{inputenc}
\usepackage[activeacute, spanish]{babel}
\usepackage[dvips]{graphicx}
\selectlanguage{spanish}

@@

In order to reduce noise in the corpus, we filtered all the letters and works that were comparatively little. Our information value theory doesn't work very well with texts with little repetition of words, so we decided to remove texts with less than 2000 words.

\begin{figure}
\centerline{\includegraphics[width=.4\textwidth]{figures/tokens_per_year.eps}}
\caption{Number of tokens per year}\label{afoto}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=.4\textwidth]{figures/hist_tokens_small_works.eps}}
\caption{Distribution of works with respect to size (small works)}\label{afoto}
\end{figure}

\begin{figure}
\centerline{\includegraphics[width=.4\textwidth]{figures/hist_tokens_big_works.eps}}
\caption{Distribution of works with respect to size (big works)}\label{afoto}
\end{figure}

%*Números (obras totales obtenidas, promedio tokens)
\subsection{Information Value Framework}
%
%*Aclarar settings de Zannette
%*Maximización, ventanas
%*Cálculo paralelo
%*Ajustes de parametros para que concuerden con los resultados de zanette
%*doc.top_words()
%  representación como set de palabras ponderadas por documento.

@@

% *WordnetAnalyzer
%   *Synset
%   *path, lch, wup
% *judge_word
% *judge_doc
% *judge_year
% Dado un conjunto de palabras, definimos la distancia de una palabra a este conjunto como 
% 
S(x, C) = max { ... }
